A quantitative framework for investigating the reliability of empirical network construction

### 2018-10-30 manuscript/reply_to_reviewers.tex

\documentclass[12pt]{letter}

\usepackage[britdate]{LiU-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\begin{document}

\newpage

\setcounter{page}{1}

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

@@

	\begin{refquote}
	Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address this. Reviewer 2's comments take a different view of the purpose and scope of the manuscript than the other reviewers; we respect their ideas but feel that some are beyond the scope of the present manuscript. We therefore prioritise comments by the other three Reviewers and hope that, by addressing these, the purpose of our manuscript becomes clearer and our changes will at least partially satisfy Reviewer 2.

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

@@

		Literature suggestions:

	Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763

	Bartomeus, I. (2013). Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. PLoS ONE, 8(7), 1–9. doi:10.1371/journal.pone.0069200
	Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D. B. (2016). The structure of probabilistic networks. Methods in Ecology and Evolution, 7(3), 303–312. doi:10.1111/2041-210X.12468
	Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
	Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
	Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D. (2013). Inferring food web structure from predator-prey body size relationships. Methods in Ecology and Evolution, 4(11), 1083–1090. doi:10.1111/2041-210X.12103
	Wells, K., & O’Hara, R. B. (2013). Species interactions: Estimating per-individual interaction strength and covariates before simplifying data into per-species ecological networks. Methods in Ecology and Evolution, 4(1), 1–8. doi:10.1111/j.2041-210x.2012.00249.x

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Referee \#2}
% ---------------------------------------

@@

	I do not know what to do with this.

	\begin{refquote}
	The paper by A.Cirtwill and colleagues tackles a very interesting problem, quantifying the uncertainity of interactions, using three levels of nested uncertainity. The authors proposed a bayesian framework to obtain estimate of the parameters of the model and show the results of their approach on a recent dataset. The question of disentangling the true presence/absence of an interaction given a series of observations (replicates) is of primary interest and, seen in this light, the paper is tackling one of the hottest topics in the field.

@@

Reviewer: 3

Comments to the Corresponding Author
Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved:

1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realize that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.  Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.

4. Misunderstanding of our point about sampling effort

	\textbf{R:} We believe that the Reviewer has badly misunderstood the point of our comments on sampling effort. We (like other sane people) would never suggest that researchers intensively sample less intensively. We assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would have no effect. We now state these assumptions explicitly. Moreover, we believe that increased sampling effort will not reduce all sources of sampling uncertainty. For example, interactions that are not detectable using a particular sampling methodology will not be included by sampling more intensively using that method. Our comments about sampling were intended to draw attention to this and other issues, not to say that sampling is bad. Indeed, we point out that a high degree of sampling is necessary to detect rare species and to gain confidence that any two co-occurring species do not interact. Sampling is a valuable tool that happens not to solve the problems we are most interested here. To be absolutely clear about this to future readers we have added a box (Box 1) where we discuss why sampling alone will not solve problems about uncertainty. We hope that this box will make our (pro-sampling) stance clearer to the Reviewer and to future readers.

	\textbf{R:} Of course sampling more does not lead to less understanding. It can, however, reveal knowledge gaps (as when a rare species is detected, revealing our ignorance of its interactions). This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more "false zeros" as species about which we know little are added to the network.

	\textbf{R:} I do not know how the Reviewer assumes that we are against repeat sampling when this is, in fact, one of the core parts of our approach. Our point here is that some species (e.g., cryptic or difficult-to-identify species) and interactions (e.g., brief visits of pollinators to plants) are difficult to detect and may be missed even with multiple sampling. If a rare species is only detected in one sampling round, then the repeated sampling necessarily tells us little about its interactions. For species which are frequently detected, we absolutely learn about the detection probability of their interactions with repeated sampling.

	\textbf{R:} We agree that it is dangerous to suggest that anyone sample less, that is why we have not done so. We argue only that the amount of sampling required to be confident that co-occurring species do not interact is large -- likely beyond what is feasible for speciose systems given the limited resources available to many researchers. Sampling across most network studies is almost certainly not sufficient, but data which would allow readers to judge this (i.e., number of times each species is observed, independent of numbers of observed interactions) is not generally provided. We chose to be more charitable than the Reviewer and assume that those compiling empirical networks are sampling as much as possible given the constraints of their system and available resources. Infite sampling would, of course, be the best option but it is unlikely that researchers will be able to perpetually increase sampling.

@@

	Line 338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad…  At the end of the paragraph it seems it isn’t so great to sample more because you end up with these annoying “0” values…??????

Below I provide specific comments

	Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation.

	\textbf{R:} We have softened this statement to say that empirical networks are "often limited" and hope that this rephrasing will not offend those who are working to include variation in their descriptions.

		\begin{quotation}
			Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
		\end{quotation}

@@

Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!

Line 86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.

	Line 73, 87.  Maybe the idea that some uncertainty is “inevitable” should not be repeated in multiple sections.  Either find a different way of saying it – or state it in your introductory paragraph and then don’t keep repeating.

	\textbf{R:} We have rephrased the paragraph about detection uncertainty. The last line now reads:

		\begin{quotation}

			Until these gaps are filled, some interaction uncertainty will remain.

		\end{quotation}

@@

Introduction – T. Poisot and colleagues have done a lot of relevant work in this area, but I felt there was undue reference to their work in comparison with other relevant work. There were some obvious papers (e.g. sampling by Jordano, forbidden links by various others) that were not cited. A broader perspective on the literature would, I think, help the authors appreciate the value of their paper and the need to ensure that it is fully understandable and of practical use.

L36ff The authors should note the value of weighted metrics in taking account of sampling biases.

L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.

\textbf{R:} Unfortunately, the use of binary networks is not as rare as the Reviewer thinks, particularly in food webs where it is often difficult to quantify interaction strengths or frequencies in the field. We absolutely agree that weighted networks are much more valuable when they are available but did not wish to exclude those without such data. [[Do we want to add a bit of non-binary stuff or just make it clearer that we are talking about feasibility and that probabilities of occurrance could be layered on later?]]

@@

L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.

Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. [[So we need to state more clearly that we cannot distinguish these after the fact.]]

L76ff ‘Process uncertainty’ is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’. The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. [[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]

\textbf{R:} It seems our descriptions of interaction uncertainty and process uncertainty were both unclear, as the Reviewer has badly mixed them up. We have expanded the paragraph introducing the different levels of uncertainty to include plain-language questions addressed by each level of uncertainty; hopefully this will help to avoid confusion at the outset.

	\begin{quotation}

		As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}). These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".

	\end{quotation}

We have also added a paragraph to explain the interaction uncertainty explicitly \emph{does not} depend on co-occurrence; only on species traits. The Reviewer is not correct that habitat belongs in interaction uncertainty as species which do not currently share a habitat might still interact if one is introduced into the other's habitat (for example). We now state this explicitly.

	\begin{quotation}

		Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur. Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}. In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.

	\end{quotation}

Process uncertainty covers factors which prevent an interaction which \emph{can occur} from actually occurring at particular places/times. This includes factors which mean that two potentially interactive species do not co-occur (e.g., habitat requirements) as well as factors which reduce interaction probability between co-occurring species (weather, abundances, etc.). We have rephrased the first line of this section to make this explicit.

	\begin{quotation}

		Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time.

	\end{quotation}

Weather likely affects both process uncertainty and detection uncertainty. For pollination, pollinators are much less likely to interact in the rain (process uncertainty) and the lower visibility may mean that some interactions which do occur are missed (detection uncertainty). We have added a paragraph in the section describing detection uncertainty to make it clear that some external factors can affect multiple types of uncertainty.

	\begin{quotation}

		Note that some exteral factors can affect both process and detection uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}. Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.

	\end{quotation}

The Reviewer is correct that increasing sampling effort to include more interaction-promoting weather, sites, etc. will reduce process uncertainty. It would also be possible to gerrymander the spatial scale of sampling such that non-interacting species do not co-occur, but we would not advocate selecting a study site to avoid particular species. The appropriate spatial and temporal scale of sampling is an important question, but it is not the question we are addressing here. Instead, we have added a line to include the Reviewer's point that expanded sampling can help to address process uncertainty and left it at that.

	\begin{quotation}

	Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit.

	\end{quotation}

@@

L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).

\textbf{R:} Long-term interactions may be easier to detect, but we do not see how this affects process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section. Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interacitons such as gall-forming.

	\begin{quotation}

		Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactoins will be missed.

	\end{quotation}

### 2018-10-30 manuscript/CI_interactions.tex
corrections

    Representing an ecological community as a network summarises both species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are usually limited to static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Worse, variability in community composition and interactions may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or because of individual preferences~\citep{Fodrie2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. The detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}).

@@

          First, and most fundamentally, a pair of species may or may not have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur. In such cases, $\lambda = 0$ and there is no uncertainty.

          Most species pairs, however, do not have traits that absolutely prevent an interaction. This means that it is generally unclear whether an unobserved interaction is impossible or simply a rare phenomenon with $\lambda>0$. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}. Some interaction uncertainty is therefore inevitable.

        \subsubsection*{Process uncertainty}

         Even a feasible interaction, i.e. $L=1$, still may not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat. We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). In the field, however, process uncertainty is likely inevitable.

         One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). The absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Because we cannot separate these possibilities, repeated sampling fails to satisfactorily address the uncertainty inherent in empirical networks.

>>>>

    Representing an ecological community as a network summarises both species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Worse, variability in community composition and interactions may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015} or individual preferences~\citep{Fodrie2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012,Bartomeus,others}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these efforts, we currently lack the quantitative methodology to deal with uncertainty generated by spatiotemporal variation in ecological interactions and by limited sampling. [[cite previous attempts]] Even in well-sampled networks, uneven sampling across species can lead to the inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms}). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. In terms of the ones and zeros in a binary interaction matrix, we know that the ones are true but we cannot be sure that the zeros reflect interactions which actually do not occur. The detection of any interaction is a stochastic process. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{conceptual_fig}). These levels roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact at this site/time?" and "Do we observe the interaction?".

@@

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$~\citep{Dom?}. In some cases the traits prohibiting an interaction are known. A potential prey may be too large, small, or well-armoured for a predator to attack, or it might be toxic or non-nutritious (e.g., large carnivores do not consume plants because they cannot digest them and typically do not consume small insects because of the large handling cost relative to the energy gained from tiny prey). Where the critical traits are known and mean that an interaction is unfeasbile, $\lambda = 0$ and there is no uncertainty about associated zeros in an interaction matrix.

          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{} and herbivores may consume animal prey when it becomes accessible~\citep{}. These examples show that we often cannot say that an interaction absolutely does not occur. Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and an associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some interaction uncertainty will remain.

          Note that interaction uncertainty does not depend upon whether species $i$ and $j$ actually co-occur. Ecologists are often interested in predicting which species are likely to interact following an introduction~\citep{} or range shift~\citep{}. In such cases, models based on trait matching can give some information about $\lambda$ while past co-occurance will, of course, not yield much insight.

        \subsubsection*{Process uncertainty} [[Maybe need to rename]]

          Assuming that an interaction is feasible (i.e., $L=1$; species traits do not prohibit an interaction if they should co-occur), an interaction still not occur at a particular place or time. This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction. For example, a pollination interaction may not occur on a rainy day or a rare galler may not parasitize a rare plant because they do not encounter each other. 
          We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi$=1 except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.

          This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce process uncertainty if resource constraints permit. In the field, however, process uncertainty is likely inevitable as long as local conditions are not constant during sampling.

         % One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017-wrong one?} used repeated sampling to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty.[[This apparently confused R3]] While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactoins will be missed.

          To sum up, the absence of an interaction on a given day could therefore be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect both process and detection uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes (process uncertainty)~\citep{}. Interactions involving rare species are also less likely to be detected (detection uncertainty), unless more sampling effort is focused on rare than common species~\citep{}. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also reduce visibility and therefore increase detection uncertainty.
